### 2023-09-04 paper/sec-introduction.tex
Added mention that xFitter is also open-source + small typo fix

Here we bridge this gap by quantifying
the expected impact of  neutrino DIS structure functions at the LHC on proton and nuclear PDFs.
%
To this end, we produce simulations for  FASER$\nu$ and SND@LHC at Run III 
as well as for the proposed FPF experiments~\cite{Anchordoqui:2021ghd,Feng:2022inv,Batell:2021blf,Batell:2021aja}, FLArE, AdvSND, and FASER$\nu$2.
%
For each experiment, we determine the expected event yields in bins of $(x,Q^2,E_\nu)$
satisfying acceptance and selection cuts,
generate pseudo-data for  inclusive and charm 
structure functions, 
and estimate their dominant systematic uncertainties.
%
Subsequently, we study their impact on the proton and nuclear PDFs by means of both the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
of  PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} (for protons) and EPPS21~\cite{Eskola:2021nhw}
(for tungsten nuclei)
within {\sc\small xFitter}~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web},
as well as with the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.

Our analysis reveals that  LHC neutrino structure functions can provide  stringent constraints
on the light quark and antiquark PDFs, specially on the up and down
valence quarks and on strangeness, as compared to state-of-the-art global analyses.
%
We also  find that accounting for the main systematic uncertainties does not significantly
degrade the sensitivity achieved by baseline fits considering only statistical errors.
%
We quantify the impact in our results of charm-tagged structure functions (large), study the relevance
of final-state lepton-charge identification capabilities (moderate), and compare the constraints
provided by different experiments (finding that the overall sensitivity is dominated by FASER$\nu$2).
%
We also study the implications of the resulting improvement in PDF precision
on core processes at the HL-LHC, finding a theory error reduction
of up to a factor two for selected  Higgs and gauge boson production
cross-sections.

>>>>

Here we bridge this gap by quantifying
the expected impact of  neutrino DIS structure functions at the LHC on proton and nuclear PDFs.
%
To this end, we produce simulations for  FASER$\nu$ and SND@LHC at Run III 
as well as for the proposed FPF experiments~\cite{Anchordoqui:2021ghd,Feng:2022inv,Batell:2021blf,Batell:2021aja}, FLArE, AdvSND, and FASER$\nu$2.
%
For each experiment, we determine the expected event yields in bins of $(x,Q^2,E_\nu)$
satisfying acceptance and selection cuts,
generate pseudo-data for  inclusive and charm 
structure functions, 
and estimate their dominant systematic uncertainties.
%
Subsequently, we study their impact on the proton and nuclear PDFs by means of both the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
of  PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} (for protons) and EPPS21~\cite{Eskola:2021nhw}
(for tungsten nuclei)
within the {\sc\small xFitter}~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web} open-source QCD analysis framework,
as well as with the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.

Our analysis reveals that  LHC neutrino structure functions can provide  stringent constraints
on the light quark and antiquark PDFs, especially on the up and down
valence quarks and on strangeness, as compared to state-of-the-art global analyses.
%
We also  find that accounting for the main systematic uncertainties does not significantly
degrade the sensitivity achieved by baseline fits considering only statistical errors.
%
We quantify the impact in our results of charm-tagged structure functions (large), study the relevance
of final-state lepton-charge identification capabilities (moderate), and compare the constraints
provided by different experiments (finding that the overall sensitivity is dominated by FASER$\nu$2).
%
We also study the implications of the resulting improvement in PDF precision
on core processes at the HL-LHC, finding a theory error reduction
of up to a factor two for selected  Higgs and gauge boson production
cross-sections.
